%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\clearpage
\cvsection{Cover Letter}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\begin{cvparagraph}

%---------------------------------------------------------

\vspace{4ex}

Dear Hiring Team,

\vspace{2ex}


Throughout my 15+ years in technology innovation, I have led and executed successful initiatives across AI, data architecture, e-commerce, robotics, and mobile applications. My experience spans start-ups, global corporate headquarters, and multi-million Euro publicly funded R\&D projects. Focusing on AI and data, key highlights include:

\vspace{1ex}


\begin{itemize}

\item \urlll{https://github.com/n42r/muze-ai}{\textbf{MuzeAI}} (2023-24): Built an open-source LLM-powered music recommendation prototype leveraging Spotify data, receiving promising pilot feedback.

\item \urlll{https://n42r.github.io/phd}{\textbf{The Basin Network}} (2020-2023): Invented a next-generation data architecture for ML teams to share and remix data across enterprises, earning a PhD and two publications.

\item \urlll{https://github.com/simutool}{\textbf{SIMUTOOL Data Management SaaS}} (2015-19): Led a four-year initiative to build a SaaS that optimized operational efficiency by 30\% for a €3.5M EU-funded aerospace manufacturing consortium.

\item \urlll{https://n42r.github.io/tw}{\textbf{Tawla iOS mobile board game}} (2011-13): Led development of AI players for an iOS backgammon game in a B2C environment, increasing engagement and sales.

\item \textbf{RoboCup AI Soccer Team} (2010‑11): Co‑founded and co‑led a team of 10 to develop an AI‑driven soccer software that qualified for the 2012 International RoboCup finals qualification round.

%. Designed the critical ball‑passing algorithm using Markov chain modeling (a field I had no prior experience in) and authored the position paper that secured our spot in the 2012 RoboCup finals qualification round.

%\item I co-founded and co-led a team of 10 to to build a AI software to play soccer to compete in the International RoboCup competition. I designed the most technically complex and critical component of the project, the ball passing algorithm, using markov chain modeling (a subject I had no prior experience in), and wrote the position paper which earned us a spot in the 2012 RoboCup finals qualification round, \textbf{2011-12}.

%\item I invented two frameworks to help make robots more intelligent and published my findings in top-tier AI conferences (ECAI \& KI). one was a influenced by the idea of \urlll{https://ebooks.iospress.nl/volumearticle/6006}{\textbf{short-term memory in humans}}, and the other solved a complex philosophical problem related to \urlll{https://doi.org/10.1007/978-3-642-16111-7\_14}{\textbf{robot perception and visual illusion}}, . Earned a masters degree with a grade of excellent in Computer Science and Engineering for it, \textbf{2009-2010}.

%\item I built a solution that integrated structured background knowledge into case-based reasoning, with use-cases in early breast cancer detection and heart attack diagnosis, and published a paper about it, earning a bachelors degree with a grade of excellent for it, \textbf{2008} 

%\item Two projects I played a critical role in during my undergraduate years (building a robot car to navigate mazes and building a game in Java/Java 3D) won top university competition awards \textbf{2005-2007}.

\end{itemize}

\vspace{2ex}

Currently, as Lead Solutions Architect at PUMA’s Global E-Commerce Engineering, I have:

%In recent years, my interests and focus have moved to building innovative organizations. Since I joined PUMA I have initiated two high profile, high value organizations. 
%\vspace{1ex}

\begin{itemize}

\item Founded and led an organization of two teams, improving PUMA.com’s performance by 20\%.
\item Established the Technical Cats of E-Commerce initiative, fostering technical design and innovation.

\end{itemize}


%My background aligns with this role not only in my technical expertise but also in my ability to bridge AI strategy with business impact. I have led AI-driven initiatives, from prototyping an AI-powered music recommendation system to advising on AI adoption in e-commerce. 

%My wide ranging experiences in data architecture, solution design, and cross-functional leadership has prepared me to define and implement AI strategies at an enterprise level. While I may not have managed large AI/ML teams directly, I have built AI-centric products and collaborated with stakeholders to drive innovation—skills that are crucial in leading AI initiatives across a global organization. The opportunity to shape the AI vision in a newly founded division excites me, as I thrive in building strategic roadmaps and aligning emerging technologies with business goals. The opportunity to shape the AI vision in a newly founded division excites me, as I thrive in building strategic roadmaps and aligning emerging technologies with business goals.

\vspace{2ex}


My leadership philosophy is rooted in exploration, experimentation, and disciplined execution—without premature commitments to unproven directions. I believe in rapidly testing diverse approaches, recognizing early when to pivot, and driving innovation with a deep understanding of both technology and organizational dynamics.


\vspace{1ex}


In an industry where disruptive breakthroughs often emerge unpredictably, the ability to navigate ambiguity while systematically identifying high-value opportunities is key. My experience--spanning AI, data architecture, e-commerce, and R\&D--has reinforced this mindset. As Director of AI and Machine Learning, I can bring this approach to PUMA, ensuring that our AI strategy is not only innovative but also pragmatic, scalable, and impactful for the business.







\vspace{5ex}

Sincerely,\\
	
Nasr Kasrin

%\end{cvparagraph}
