%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


  \cventry
    {Open Source Software} % Project Type
    {Muze AI} % Project Name
    {2023 - 2024} % URL
    {\urll{github.com/n42r/muze-ai}} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Developed an early AI/LLM music discovery tool, bypassing the reliance on Spotify's music recommendation metadata.}
	      \end{cvitems}
    }

%---------------------------------------------------------


  \cventry
    {Open Source Software} % Project Type
    {Guestrrday} % Project Name
    {2022 - 2023} % URL
    {\urll{github.com/n42r/guestrrday}} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Engineered an open-source music tagging tool capable of processing over 20,000 items, enhancing music organization and accessibility.}
	      \end{cvitems}
    }


%---------------------------------------------------------


  \cventry
    {Architectural Model} % Project Type
    {The Basin Network (Doctoral Project)} % Project Name
    {2019 - 2023} % URL
    {\urll{n42r.github.io/phd}} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Invented a novel architectural pattern for data cataloging, improving on data mesh and data space models in 3 respects: precision, level of detail, and generalization, culminating in the award of a PhD with distinction and 2 published papers.}
%			\item {Standardized the pattern to facilitate data exchange, data governance, interoperability, and effective management of data as an asset, .}
			%\item {Published findings in 2 journals, contributing to advancements in the field of data management.}
	      \end{cvitems}
    }


%---------------------------------------------------------

  \cventry
    {SaaS (European Union Publicly Funded Project)} % Project Type
    {SIMUTOOL Data Lake} % Project Name
    {2015 - 2019} % URL
    {\urll{github.com/simutool}} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Built a data lake SaaS for a consortium of 8 manufacturing companies, cutting turnover time by 30\% by fostering data-driven cooperation.} 
%			\item {Developed the back-end server (python, Flask, WSGI, REST, Neo4J, Semantic Data Modeling, RDF, JSON-LD) as well as a CRUD web application (Apache Server, web2py framework, HTML, CSS, MySQL).}
			%\item {Enabled streamlined data sharing \& exchange in a consortium of 8 companies}
			%\item {Designed the application architecture, developed the back-end, and supervised a team in creating client applications, contributing significantly to the project's success, as recognized by an expert panel appointed by the European Commission.}
%			\item{Designed the application, constructed the back-end, and guided client development, pivotal to the project's success as acknowledged by an EC-appointed panel.}
	%		\item {Designed the application, constructed the back-end, and guided client development, pivotal to the project's success as per an EC-appointed panel.}
			\item {Designed the app, built the back-end, and led client development, crucial to project success as acknowledged by an EC-appointed panel.}
	      \end{cvitems}
%	      90\% user satisfaction 
    }
    

%---------------------------------------------------------


  \cventry
    {Social Network/iOS Mobile App (B2C)} % Project Type
    {Greetings Studio} % Project Name
    {2012 - 2014} % URL
    {\urll{n42r.github.io/gs}} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
				\item {Directed the development of an E-greeting card social network and mobile app, optimizing user engagement leading to 10-fold growth in users.}
				\item {Redesigned the architecture, leading to a 15\% reduction in development time originally due to circumventing technical architecture debt.}
	      \end{cvitems}
    }
    
    
%---------------------------------------------------------


  \cventry
    {Game/iOS Mobile App (B2C)} % Project Type
    {Tawla (Backgammon Board Game)} % Project Name
    {2011 - 2013} % URL
    {\urll{n42r.github.io/tw}} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
	          	\item {Elevated app ratings from 3 to 4.5/5 stars by the implementation of advanced AI players, enhancing gameplay dynamics.}
				\item {Achieved a 10\% increase in positive reviews due to building a sophisticated random number generator for the die, which improved gameplay.}
	      \end{cvitems}
    }
    
    

%---------------------------------------------------------


  \cventry
    {AI/Robotics software to compete in the 2011 International RoboCup Competition} % Project Type
    {ArtSapiens 2D Soccer} % Project Name
    {2010 - 2011} % URL
    {\urll{ssim.robocup.org}} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Co-founded and co-led a team of 10 that developed robotics/AI software which qualified to compete in the 2011 RoboCup Competition.}%, which qualifications and earned a spot in 2011 competition in Kuala Lumpur, Malaysia.}
	      \end{cvitems}
    }
    
    
%---------------------------------------------------------

\end{cventries}
