%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
%\clearpage 
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}




%---------------------------------------------------------


    
        
  \cventry
    {PUMA SE, Global E-commerce Engineering}  % Organization
    {Lead Solutions Architect} % Job title
    {2024 - present} % Date(s)
    {Herzogenaurach, Germany} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Founded and led an organization of two teams (4+4+2) which improved PUMA.com's performance by 25\%.}
		\item {Established (+ composed charter) of Ecomm Technical Cats (ETC) organization with a Tech Design Board \& innovation forum.}
		\item {Led a war-room-like workshop of 15 technical experts to solve a complex problem causing PUMA NA to loose 9/10 orders on product launches.}
		\item {Investigated AI/LLMs for supporting software development and devised a initial framework for embedding LLMs in SE.}						
		%\item {Led a team to migrate a global CRM system for PUMA India (Emarsys to CleverTap).}
		%\item {Preemptively identified and solved a complex architectural problem jeopardizing a major system migration in PUMA Latin America.}
    \end{cvitems}
    }
    

%---------------------------------------------------------


    
        
  \cventry
    {Freelance}   % Organization
    {Co-Founder | CTO  | Data Architecture Scientist | Prototyper} % Job title
    {2021 - 2024} % Date(s)
    {Bamberg, Germany} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Co-founding a startup for AI/LLM-driven solutions \& building prototypes for products with millions of potential users (left when joining PUMA).}
		\item {Developed an AI-driven music recommendation prototype utilizing open-source LLMs, with positive feedback from pilot users (\textbf{MuzeAI}, below).}
		\item {Researched and invented a next-gen data architecture (post-data mesh) for exchanging data across organizations (\& awarded a PhD for it).}
    \end{cvitems}
    }
    


%---------------------------------------------------------

    
        
  \cventry
    {University of Bamberg (EU-Funded Manufacturing Project)} % Organization
%    {Research Associate (Lead Data Solutions Engineer (SaaS) | Principal Software Architect | Senior Project Manager (Data Solutions))} % Job title
    {Research Associate (Team Lead | Dev Lead | Architect | Data Solutions Engineer)} % Job title
    {2015 - 2020} % Date(s)
    {Bamberg, Germany} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Led a 4-year project to develop a data management SaaS platform which optimized operational efficiency by 30\% in a €3.5 million 8-company EU aerospace manufacturing project \see{github.com/simutool}.}
		\item {Engineered a read-heavy SaaS, ensuring seamless operations and future-proof cloud-native architecture (ex., docker, stateless nodes).}
      \end{cvitems}
    }
    

%---------------------------------------------------------


%  \cventry
%    {University of Technology Twintech} % Job title
%    {Assistant Dean / Lecturer} % Organization
%    {2013 - 2015} % Location
%    {Sanaa, Yemen} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%		\item {Managed the IT and Multimedia faculties, reporting to the university president}
%		\item {Modernized the curriculum by leading a curriculum development initiative for the Business IT and Multimedia faculties}
%		\item {Taught several Courses: \emph{Software Analysis}, \emph{Human-Computer Interaction}, \emph{Information Design}, etc}
%      \end{cvitems}
%    }

%---------------------------------------------------------


  \cventry
    {TayaIT} % Organization
    {R\&D Engineer (AI) | Team Lead | Software Architect} % Job title
    {2011 - 2014} % Date(s)
    {Cairo, Egypt} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Built 2 AI players (java, C) for a mobile board game (backgammon), and lead a team of two R\&D engineers to port them to Objective-C.}
		\item {Led a software engineering team in building 2 iOS mobile apps, driving rankings to 4.5/5 and increasing user engagement by 10.}
		\item {Reduced feedback-development cycle times by 25\% by coordinating cross-functional collaboration between technical, business, and UI/UX.}
		\item {Saved the company 10-man months by investigating emerging trends and alternative paths and advising the CEO in fruitful directions.}
      \end{cvitems}
    }

%---------------------------------------------------------


%\cventry{2008 -- 2012}{Teaching Assistant}{The German University in Cairo (GUC)}{Cairo}{Egypt}{
%\begin{itemize}
%\item Taught 10 hours per week of tutorials, interfacing with 150 new students per semester.
%\item Courses: \emph{Introduction to Artificial Intelligence}, \emph{Introduction to Computer Science}, \emph{Introduction to Computer Programming}. 
%\end{itemize}}


\end{cventries}

\vspace{-0.5ex}

